Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-01 lineages_18Q3.Rmd
added g2p and SO files from Dan, new plots/analyses

Load libraries.
```{r}
library(NMF)
library(ggpubr)
library(ggsignif)
library(rowr)
library(data.table)
library(CePa)
library(plyr)
library(tidyverse)
library(magrittr)
library(matrixStats)
library(parallel)
library(kableExtra)
library(gridExtra)
library(broom)
library(glmnet)
library(devtools)
library(reshape2)
library(caret)
library(bsselectR)
library(ComplexHeatmap)
library(circlize)
```

@@

```{r}
crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_gene.rds")

@@

```{r}
crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_gene.rds")

@@

```{r}
crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")

@@

```{r}
crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_lineage.rds")

@@

```{r}
crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_lineage.rds")

@@

```{r}
crispr_signif_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_lineage.rds")

@@

```{r}
crispr_signif_allmut_del <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_gene.rds")

@@

```{r}
crispr_signif_allmut_nonsilent <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_gene.rds")

@@

```{r}
crispr_signif_allmut_delmis <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissense_gene.rds")

@@

```{r}
crispr_signif_allmut_del_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_lineage.rds")

@@

```{r}
crispr_signif_allmut_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_lineage.rds")

@@

```{r}
crispr_signif_allmut_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissens_lineage.rds")

@@

```{r fig.height=5, fig.width=12}
genes_lvlA <- c("EGFR", "KRAS", "BRAF", "NRAS", "ERBB2", "MET", "ALK", "AKT1", "PDGFRA", "RET")
crispr_ptmuts_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
crispr_ptmuts_lvlA$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA$Hugo_Symbol, levels = genes_lvlA)
crispr_ptmuts_lvlA_color <- as.character(crispr_ptmuts_lvlA$Color_DeleteriousMissense)
names(crispr_ptmuts_lvlA_color) <- crispr_ptmuts_lvlA$Mutation_Status_DeleteriousMissense

crispr_ptmuts_lvlA_plot <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Hugo_Symbol, y = Score)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_violin(mapping = aes(fill = Mutation_Status_DeleteriousMissense), alpha = 0.7, position = position_dodge(0.85)) +
  geom_boxplot(mapping = aes(color = Mutation_Status_DeleteriousMissense), position = position_dodge(0.85), width = 0.1) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
  scale_color_manual(values = c("black", "black")) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(1, 0), legend.position = c(1, 0), legend.box.margin = margin(c(10, 10, 10, 10))) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Gene")
crispr_ptmuts_lvlA_plot
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 12, height = 5, units = "in")

crispr_ptmuts_lvlA_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_DeleteriousMissense, y = Score)) +
  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_violin(mapping = aes(fill = Mutation_Status_DeleteriousMissense), alpha = 0.7, position = position_dodge(0.85)) +
  geom_boxplot(mapping = aes(color = Mutation_Status_DeleteriousMissense), position = position_dodge(0.85), width = 0.1) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
  scale_color_manual(values = c("black", "black")) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.5, 0), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_plot_faceted
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 12, height = 5, units = "in")
```

@@

```{r fig.height=5, fig.width=12}
g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", row.names = 1, header = TRUE), Evidence.Level == "A")
maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
crispr_g2p_indications <- merge(maf_g2p_indications, crispr_data_ptmuts, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"))
dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
crispr_g2p_indications <- filter(crispr_g2p_indications, is.na(n))

@@

>>>>

Load libraries.
```{r}
library(NMF)
library(ggpubr)
library(ggsignif)
library(rowr)
library(data.table)
library(CePa)
library(plyr)
library(tidyverse)
library(magrittr)
library(matrixStats)
library(parallel)
library(kableExtra)
library(gridExtra)
library(broom)
library(glmnet)
library(devtools)
library(reshape2)
library(caret)
library(bsselectR)
library(ComplexHeatmap)
library(circlize)
library(jsonlite)
```

@@

```{r, eval=FALSE}
crispr_signif_del <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_gene.rds")

@@

```{r, eval=TRUE}
crispr_signif_nonsilent <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_gene.rds")

@@

```{r, eval=FALSE}
crispr_signif_delmis <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_gene.rds")

@@

```{r, eval=FALSE}
crispr_signif_del_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleterious_lineage.rds")

@@

```{r, eval=FALSE}
crispr_signif_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_nonsilent_lineage.rds")

@@

```{r, eval=FALSE}
crispr_signif_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_ptmuts_deleteriousmissense_lineage.rds")

@@

```{r, eval=FALSE}
crispr_signif_allmut_del <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_gene.rds")

@@

```{r, eval=FALSE}
crispr_signif_allmut_nonsilent <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_gene.rds")

@@

```{r, eval=FALSE}
crispr_signif_allmut_delmis <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissense_gene.rds")

@@

```{r, eval=FALSE}
crispr_signif_allmut_del_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleterious_lineage.rds")

@@

```{r, eval=FALSE}
crispr_signif_allmut_nonsilent_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_nonsilent_lineage.rds")

@@

```{r, eval=FALSE}
crispr_signif_allmut_delmis_lineage <- readRDS("./data_munging/rds/crispr_signif_allmut_deleteriousmissens_lineage.rds")

@@

```{r fig.height=5, fig.width=20}
genes_lvlA <- c("ABL1", "ALK", "AR", "ATM", "BRAF", "BRCA1", "BRCA2", "CDKN2A", "DNMT3A", "DPYD", "EGFR", "ERBB2", "ERBB3", "FGFR2", "FLT3", "JAK2", "KIT", "KRAS", "MET", "NOTCH1", "NOTCH2", "NRAS", "PDGFRA", "PDGFRB", "PIK3CA", "PML", "PTCH1", "RET", "ROS1", "SF3B1", "SMO", "TP53", "TSC1")
crispr_ptmuts_lvlA <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA)
crispr_ptmuts_lvlA$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA$Hugo_Symbol, levels = genes_lvlA)
crispr_ptmuts_lvlA_color <- as.character(crispr_ptmuts_lvlA$Color_Nonsilent)
names(crispr_ptmuts_lvlA_color) <- crispr_ptmuts_lvlA$Mutation_Status_Nonsilent

crispr_ptmuts_lvlA_plot <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Hugo_Symbol, y = Score)) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
  guides(color = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10))) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Gene")
crispr_ptmuts_lvlA_plot
ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot.png", crispr_ptmuts_lvlA_plot, device = "png", width = 20, height = 5, units = "in")

crispr_ptmuts_lvlA_plot_faceted <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score)) +
  facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
  geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
  geom_boxplot(mapping = aes(fill = Mutation_Status_Nonsilent), position = position_dodge(0.85)) +
  scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
  guides(color = FALSE) +
  theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
  labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
crispr_ptmuts_lvlA_plot_faceted
ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted.png", crispr_ptmuts_lvlA_plot_faceted, device = "png", width = 20, height = 5, units = "in")

# label_text <- crispr_signif_nonsilent$p.signif.adj
# names(label_text) <- crispr_signif_nonsilent$Hugo_Symbol
# label_text <- label_text[genes_lvlA]
# 
# crispr_ptmuts_lvlA_plot_faceted_truncated <- ggplot(data = crispr_ptmuts_lvlA, aes(x = Mutation_Status_Nonsilent, y = Score, fill = Mutation_Status_Nonsilent)) +
#   facet_wrap(~ Hugo_Symbol, ncol = length(unique(crispr_ptmuts_lvlA$Hugo_Symbol))) +
#   geom_hline(yintercept = 0, lty = 2, color = "darkgray") +
#   coord_cartesian(ylim = c(-2, 2)) +
#   geom_boxplot(position = position_dodge(0.85)) +
#   scale_fill_manual(values = crispr_ptmuts_lvlA_color) +
#   geom_text(data = label_text, mapping = aes(label = p.signif.adj)) +
#   guides(color = FALSE) +
#   theme(legend.direction = "horizontal", legend.justification = c(0.5, 0), legend.position = c(0.092, 0.8), legend.box.margin = margin(c(10, 10, 10, 10)), axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank()) +
#   labs(fill = "Mutation Status", y = "CERES Score", x = "Mutation Status")
# crispr_ptmuts_lvlA_plot_faceted_truncated
# ggsave("./plots_18Q3/manuscript/crispr_ptmuts_lvlA_plot_faceted_truncated.png", crispr_ptmuts_lvlA_plot_faceted_truncated, device = "png", width = 20, height = 5, units = "in")
```

@@

```{r fig.height=5, fig.width=12}
g2p_indications <- filter(read.delim("./data_munging/data_mutation_associations_appended.csv", sep = "\t", header = TRUE), Evidence.Level == "A")
maf_g2p_indications <- filter(maf_raw, Genome_Change %in% g2p_indications$MutationName)
crispr_g2p_indications <- merge(maf_g2p_indications, crispr_data_ptmuts, by = c("Hugo_Symbol", "CCLE_Name", "Broad_ID"))
dup_g2p_indications <- filter(crispr_g2p_indications[, c("Hugo_Symbol", "CCLE_Name", "Broad_ID")] %>% group_by(Hugo_Symbol, CCLE_Name, Broad_ID) %>% tally(), n > 1)
crispr_g2p_indications <- merge(crispr_g2p_indications, dup_g2p_indications, by = c("Hugo_Symbol", "Broad_ID"), all.x = TRUE)
crispr_g2p_indications <- filter(crispr_g2p_indications, is.na(n))

@@

### JSON

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset.tsv", sep = "\t", header = TRUE, encoding="UTF-8")
test <- as.character(g2p$JSON[1])
test2 <- fromJSON(test)
```
